Estimating survival in left filtered data

### 2022-03-04 reports/resources/results.tex
Draft ready
SER

% Created by tikzDevice version 0.12.3.1 on 2021-12-10 17:23:19
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (325.21,542.02);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,542.02);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (325.21,542.02);
\end{scope}
\begin{scope}
\path[clip] ( 31.37,446.55) rectangle (306.77,536.52);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.37,446.55) rectangle (306.77,536.52);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,465.69) --
	(306.77,465.69);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,492.39) --
	(306.77,492.39);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,519.09) --
	(306.77,519.09);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,446.55) --
	( 63.65,536.52);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,446.55) --
	(129.54,536.52);

\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,446.55) --
	(195.42,536.52);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,446.55) --
	(261.31,536.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,452.35) --
	(306.77,452.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,479.04) --
	(306.77,479.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,505.74) --
	(306.77,505.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,532.44) --
	(306.77,532.44);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,446.55) --
	( 96.59,536.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,446.55) --
	(162.48,536.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,446.55) --
	(228.36,536.52);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,446.55) --
	(294.25,536.52);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,532.44) --
	( 70.24,532.44) --
	( 70.24,532.44) --
	( 83.42,532.44) --
	( 83.42,531.30) --
	( 96.59,531.30) --
	( 96.59,529.92) --
	(109.77,529.92) --
	(109.77,528.40) --
	(122.95,528.40) --
	(122.95,526.64) --
	(136.12,526.64) --
	(136.12,525.13) --
	(149.30,525.13) --
	(149.30,523.36) --
	(162.48,523.36) --
	(162.48,521.51) --
	(175.66,521.51) --
	(175.66,519.69) --
	(188.83,519.69) --
	(188.83,518.12) --
	(202.01,518.12) --
	(202.01,516.55) --
	(215.19,516.55) --
	(215.19,514.77) --
	(228.36,514.77) --
	(228.36,513.09) --
	(241.54,513.09) --
	(241.54,511.55) --
	(254.72,511.55) --
	(254.72,509.95) --
	(267.89,509.95) --
	(267.89,508.39) --
	(281.07,508.39) --
	(281.07,506.83) --
	(294.25,506.83) --
	(294.25,501.31);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,532.44) --
	( 70.24,532.44) --
	( 70.24,532.44) --
	( 83.42,532.44) --
	( 83.42,530.68) --
	( 96.59,530.68) --
	( 96.59,528.65) --
	(109.77,528.65) --
	(109.77,526.44) --
	(122.95,526.44) --
	(122.95,524.39) --
	(136.12,524.39) --
	(136.12,522.13) --
	(149.30,522.13) --
	(149.30,519.74) --
	(162.48,519.74) --
	(162.48,517.64) --
	(175.66,517.64) --
	(175.66,515.55) --
	(188.83,515.55) --
	(188.83,513.42) --
	(202.01,513.42) --
	(202.01,511.30) --
	(215.19,511.30) --
	(215.19,509.43) --
	(228.36,509.43) --
	(228.36,507.50) --
	(241.54,507.50) --
	(241.54,505.67) --
	(254.72,505.67) --
	(254.72,503.67) --
	(267.89,503.67) --
	(267.89,501.87) --
	(281.07,501.87) --
	(281.07,500.13) --
	(294.25,500.13) --
	(294.25,493.53);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,532.30) --
	( 70.24,532.30) --
	( 70.24,532.07) --
	( 83.42,532.07) --
	( 83.42,531.73) --
	( 96.59,531.73) --
	( 96.59,531.32) --
	(109.77,531.32) --
	(109.77,530.81) --
	(122.95,530.81) --
	(122.95,530.21) --
	(136.12,530.21) --
	(136.12,529.54) --
	(149.30,529.54) --
	(149.30,528.76) --
	(162.48,528.76) --
	(162.48,527.90) --
	(175.66,527.90) --
	(175.66,526.95) --
	(188.83,526.95) --
	(188.83,525.91) --
	(202.01,525.91) --
	(202.01,524.81) --
	(215.19,524.81) --
	(215.19,523.61) --
	(228.36,523.61) --
	(228.36,522.37) --
	(241.54,522.37) --
	(241.54,521.03) --
	(254.72,521.03) --
	(254.72,519.61) --
	(267.89,519.61) --
	(267.89,518.13) --
	(281.07,518.13) --
	(281.07,516.58) --
	(294.25,516.58) --
	(294.25,514.97);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,532.24) --
	( 70.24,532.24) --
	( 70.24,531.95) --
	( 83.42,531.95) --
	( 83.42,531.52) --
	( 96.59,531.52) --
	( 96.59,530.99) --
	(109.77,530.99) --
	(109.77,530.36) --
	(122.95,530.36) --
	(122.95,529.62) --
	(136.12,529.62) --
	(136.12,528.78) --
	(149.30,528.78) --
	(149.30,527.83) --
	(162.48,527.83) --
	(162.48,526.76) --
	(175.66,526.76) --
	(175.66,525.59) --
	(188.83,525.59) --
	(188.83,524.34) --
	(202.01,524.34) --
	(202.01,523.00) --
	(215.19,523.00) --
	(215.19,521.57) --
	(228.36,521.57) --
	(228.36,520.03) --
	(241.54,520.03) --
	(241.54,518.38) --
	(254.72,518.38) --
	(254.72,516.64) --
	(267.89,516.64) --
	(267.89,514.79) --
	(281.07,514.79) --
	(281.07,512.92) --
	(294.25,512.92) --
	(294.25,511.00);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,531.51) --
	( 70.24,531.51) --
	( 70.24,530.38) --
	( 83.42,530.38) --
	( 83.42,529.04) --
	( 96.59,529.04) --
	( 96.59,527.67) --
	(109.77,527.67) --
	(109.77,526.22) --
	(122.95,526.22) --
	(122.95,524.74) --
	(136.12,524.74) --
	(136.12,523.26) --
	(149.30,523.26) --
	(149.30,521.73) --
	(162.48,521.73) --
	(162.48,520.19) --
	(175.66,520.19) --
	(175.66,518.63) --
	(188.83,518.63) --
	(188.83,517.08) --
	(202.01,517.08) --
	(202.01,515.54) --
	(215.19,515.54) --
	(215.19,514.00) --
	(228.36,514.00) --
	(228.36,512.49) --
	(241.54,512.49) --
	(241.54,510.97) --
	(254.72,510.97) --
	(254.72,509.45) --
	(267.89,509.45) --
	(267.89,507.96) --
	(281.07,507.96) --
	(281.07,506.46) --
	(294.25,506.46) --
	(294.25,504.92);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,532.44) --
	( 57.06,532.44) --
	( 57.06,531.12) --
	( 70.24,531.12) --
	( 70.24,529.67) --
	( 83.42,529.67) --
	( 83.42,527.97) --
	( 96.59,527.97) --
	( 96.59,526.22) --
	(109.77,526.22) --
	(109.77,524.43) --
	(122.95,524.43) --
	(122.95,522.60) --
	(136.12,522.60) --
	(136.12,520.76) --
	(149.30,520.76) --
	(149.30,518.89) --
	(162.48,518.89) --
	(162.48,517.00) --
	(175.66,517.00) --
	(175.66,515.09) --
	(188.83,515.09) --
	(188.83,513.22) --
	(202.01,513.22) --
	(202.01,511.38) --
	(215.19,511.38) --
	(215.19,509.55) --
	(228.36,509.55) --
	(228.36,507.70) --
	(241.54,507.70) --
	(241.54,505.84) --
	(254.72,505.84) --
	(254.72,504.00) --
	(267.89,504.00) --
	(267.89,502.15) --
	(281.07,502.15) --
	(281.07,500.38) --
	(294.25,500.38) --
	(294.25,498.55);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37,446.55) rectangle (306.77,536.52);
\end{scope}
\begin{scope}
\path[clip] ( 31.37,351.08) rectangle (306.77,441.05);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.37,351.08) rectangle (306.77,441.05);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,370.22) --
	(306.77,370.22);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,396.92) --
	(306.77,396.92);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,423.62) --
	(306.77,423.62);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,351.08) --
	( 63.65,441.05);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,351.08) --
	(129.54,441.05);

\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,351.08) --
	(195.42,441.05);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,351.08) --
	(261.31,441.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,356.87) --
	(306.77,356.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,383.57) --
	(306.77,383.57);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,410.27) --
	(306.77,410.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,436.96) --
	(306.77,436.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,351.08) --
	( 96.59,441.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,351.08) --
	(162.48,441.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,351.08) --
	(228.36,441.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,351.08) --
	(294.25,441.05);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,436.96) --
	( 70.24,436.96) --
	( 70.24,436.96) --
	( 83.42,436.96) --
	( 83.42,435.74) --
	( 96.59,435.74) --
	( 96.59,434.43) --
	(109.77,434.43) --
	(109.77,432.98) --
	(122.95,432.98) --
	(122.95,431.41) --
	(136.12,431.41) --
	(136.12,429.75) --
	(149.30,429.75) --
	(149.30,427.98) --
	(162.48,427.98) --
	(162.48,426.30) --
	(175.66,426.30) --
	(175.66,424.60) --
	(188.83,424.60) --
	(188.83,422.98) --
	(202.01,422.98) --
	(202.01,421.24) --
	(215.19,421.24) --
	(215.19,419.76) --
	(228.36,419.76) --
	(228.36,418.14) --
	(241.54,418.14) --
	(241.54,416.55) --
	(254.72,416.55) --
	(254.72,414.90) --
	(267.89,414.90) --
	(267.89,413.35) --
	(281.07,413.35) --
	(281.07,411.82) --
	(294.25,411.82) --
	(294.25,406.04);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,436.96) --
	( 70.24,436.96) --
	( 70.24,436.96) --
	( 83.42,436.96) --
	( 83.42,435.30) --
	( 96.59,435.30) --
	( 96.59,433.15) --
	(109.77,433.15) --
	(109.77,430.80) --
	(122.95,430.80) --
	(122.95,428.76) --
	(136.12,428.76) --
	(136.12,426.39) --
	(149.30,426.39) --
	(149.30,424.20) --
	(162.48,424.20) --
	(162.48,422.13) --
	(175.66,422.13) --
	(175.66,420.01) --
	(188.83,420.01) --
	(188.83,417.89) --
	(202.01,417.89) --
	(202.01,415.73) --
	(215.19,415.73) --
	(215.19,413.87) --
	(228.36,413.87) --
	(228.36,412.02) --
	(241.54,412.02) --
	(241.54,410.11) --
	(254.72,410.11) --
	(254.72,408.09) --
	(267.89,408.09) --
	(267.89,406.26) --
	(281.07,406.26) --
	(281.07,404.36) --
	(294.25,404.36) --
	(294.25,397.39);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,436.96) --
	( 57.06,436.96) --
	( 57.06,436.82) --
	( 70.24,436.82) --
	( 70.24,436.59) --
	( 83.42,436.59) --
	( 83.42,436.27) --
	( 96.59,436.27) --
	( 96.59,435.85) --
	(109.77,435.85) --
	(109.77,435.33) --
	(122.95,435.33) --
	(122.95,434.71) --
	(136.12,434.71) --
	(136.12,434.01) --
	(149.30,434.01) --
	(149.30,433.22) --
	(162.48,433.22) --
	(162.48,432.33) --
	(175.66,432.33) --
	(175.66,431.35) --
	(188.83,431.35) --
	(188.83,430.30) --
	(202.01,430.30) --
	(202.01,429.17) --
	(215.19,429.17) --
	(215.19,427.95) --
	(228.36,427.95) --
	(228.36,426.66) --
	(241.54,426.66) --
	(241.54,425.30) --
	(254.72,425.30) --
	(254.72,423.86) --
	(267.89,423.86) --
	(267.89,422.34) --
	(281.07,422.34) --
	(281.07,420.76) --
	(294.25,420.76) --
	(294.25,419.13);
\definecolor{drawColor}{RGB}{0,191,196}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2022-03-04 00:12:39
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

@@

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (325.21,560.09);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,560.09);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (325.21,560.09);
\end{scope}
\begin{scope}
\path[clip] ( 31.37,463.90) rectangle (306.77,554.59);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.37,463.90) rectangle (306.77,554.59);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,483.19) --
	(306.77,483.19);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,510.10) --
	(306.77,510.10);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,537.01) --
	(306.77,537.01);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,463.90) --
	( 63.65,554.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,463.90) --
	(129.54,554.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,463.90) --
	(195.42,554.59);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,463.90) --
	(261.31,554.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,469.74) --
	(306.77,469.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,496.65) --
	(306.77,496.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,523.56) --
	(306.77,523.56);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,550.47) --
	(306.77,550.47);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,463.90) --
	( 96.59,554.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,463.90) --
	(162.48,554.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,463.90) --
	(228.36,554.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,463.90) --
	(294.25,554.59);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,550.47) --
	( 57.06,550.47) --
	( 57.06,550.47) --
	( 70.24,550.47) --
	( 70.24,550.47) --
	( 83.42,550.47) --
	( 83.42,548.70) --
	( 96.59,548.70) --
	( 96.59,546.65) --
	(109.77,546.65) --
	(109.77,544.43) --
	(122.95,544.43) --
	(122.95,542.36) --
	(136.12,542.36) --
	(136.12,540.08) --
	(149.30,540.08) --
	(149.30,537.68) --
	(162.48,537.68) --
	(162.48,535.56) --
	(175.66,535.56) --
	(175.66,533.45) --
	(188.83,533.45) --
	(188.83,531.30) --
	(202.01,531.30) --
	(202.01,529.16) --
	(215.19,529.16) --
	(215.19,527.28) --
	(228.36,527.28) --
	(228.36,525.33) --
	(241.54,525.33) --
	(241.54,523.49) --
	(254.72,523.49) --
	(254.72,521.48) --
	(267.89,521.48) --
	(267.89,519.66) --
	(281.07,519.66) --
	(281.07,517.90) --
	(294.25,517.90) --
	(294.25,511.26);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,550.47) --
	( 57.06,550.47) --
	( 57.06,550.47) --
	( 70.24,550.47) --
	( 70.24,550.47) --
	( 83.42,550.47) --
	( 83.42,549.32) --
	( 96.59,549.32) --
	( 96.59,547.94) --
	(109.77,547.94) --
	(109.77,546.41) --
	(122.95,546.41) --
	(122.95,544.63) --
	(136.12,544.63) --
	(136.12,543.11) --
	(149.30,543.11) --
	(149.30,541.33) --
	(162.48,541.33) --
	(162.48,539.45) --
	(175.66,539.45) --
	(175.66,537.62) --
	(188.83,537.62) --
	(188.83,536.04) --
	(202.01,536.04) --
	(202.01,534.45) --
	(215.19,534.45) --
	(215.19,532.67) --
	(228.36,532.67) --
	(228.36,530.97) --
	(241.54,530.97) --
	(241.54,529.42) --
	(254.72,529.42) --
	(254.72,527.80) --
	(267.89,527.80) --
	(267.89,526.23) --
	(281.07,526.23) --
	(281.07,524.66) --
	(294.25,524.66) --
	(294.25,519.09);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,550.47) --
	( 57.06,550.47) --
	( 57.06,550.37) --
	( 70.24,550.37) --
	( 70.24,550.22) --
	( 83.42,550.22) --
	( 83.42,550.01) --
	( 96.59,550.01) --
	( 96.59,549.74) --
	(109.77,549.74) --
	(109.77,549.42) --
	(122.95,549.42) --
	(122.95,549.05) --
	(136.12,549.05) --
	(136.12,548.63) --
	(149.30,548.63) --
	(149.30,548.14) --
	(162.48,548.14) --
	(162.48,547.61) --
	(175.66,547.61) --
	(175.66,547.02) --
	(188.83,547.02) --
	(188.83,546.38) --
	(202.01,546.38) --
	(202.01,545.71) --
	(215.19,545.71) --
	(215.19,544.99) --
	(228.36,544.99) --
	(228.36,544.21) --
	(241.54,544.21) --
	(241.54,543.38) --
	(254.72,543.38) --
	(254.72,542.50) --
	(267.89,542.50) --
	(267.89,541.57) --
	(281.07,541.57) --
	(281.07,540.63) --
	(294.25,540.63) --
	(294.25,539.65);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,550.47) --
	( 57.06,550.47) --
	( 57.06,550.40) --
	( 70.24,550.40) --
	( 70.24,550.29) --
	( 83.42,550.29) --
	( 83.42,550.12) --
	( 96.59,550.12) --
	( 96.59,549.91) --
	(109.77,549.91) --
	(109.77,549.65) --
	(122.95,549.65) --
	(122.95,549.35) --
	(136.12,549.35) --
	(136.12,549.01) --
	(149.30,549.01) --
	(149.30,548.62) --
	(162.48,548.62) --
	(162.48,548.18) --
	(175.66,548.18) --
	(175.66,547.70) --
	(188.83,547.70) --
	(188.83,547.18) --
	(202.01,547.18) --
	(202.01,546.62) --
	(215.19,546.62) --
	(215.19,546.02) --
	(228.36,546.02) --
	(228.36,545.39) --
	(241.54,545.39) --
	(241.54,544.72) --
	(254.72,544.72) --
	(254.72,544.00) --
	(267.89,544.00) --
	(267.89,543.26) --
	(281.07,543.26) --
	(281.07,542.47) --
	(294.25,542.47) --
	(294.25,541.66);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,550.47) --
	( 57.06,550.47) --
	( 57.06,549.81) --
	( 70.24,549.81) --
	( 70.24,549.07) --
	( 83.42,549.07) --
	( 83.42,548.22) --
	( 96.59,548.22) --
	( 96.59,547.34) --
	(109.77,547.34) --
	(109.77,546.43) --
	(122.95,546.43) --
	(122.95,545.51) --
	(136.12,545.51) --
	(136.12,544.58) --
	(149.30,544.58) --
	(149.30,543.64) --
	(162.48,543.64) --
	(162.48,542.68) --
	(175.66,542.68) --
	(175.66,541.72) --
	(188.83,541.72) --
	(188.83,540.78) --
	(202.01,540.78) --
	(202.01,539.85) --
	(215.19,539.85) --
	(215.19,538.93) --
	(228.36,538.93) --
	(228.36,537.99) --
	(241.54,537.99) --
	(241.54,537.05) --
	(254.72,537.05) --
	(254.72,536.13) --
	(267.89,536.13) --
	(267.89,535.19) --
	(281.07,535.19) --
	(281.07,534.30) --
	(294.25,534.30) --
	(294.25,533.37);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,550.47) --
	( 57.06,550.47) --
	( 57.06,550.00) --
	( 70.24,550.00) --
	( 70.24,549.43) --
	( 83.42,549.43) --
	( 83.42,548.76) --
	( 96.59,548.76) --
	( 96.59,548.07) --
	(109.77,548.07) --
	(109.77,547.34) --
	(122.95,547.34) --
	(122.95,546.59) --
	(136.12,546.59) --
	(136.12,545.84) --
	(149.30,545.84) --
	(149.30,545.07) --
	(162.48,545.07) --
	(162.48,544.29) --
	(175.66,544.29) --
	(175.66,543.51) --
	(188.83,543.51) --
	(188.83,542.72) --
	(202.01,542.72) --
	(202.01,541.95) --
	(215.19,541.95) --
	(215.19,541.17) --
	(228.36,541.17) --
	(228.36,540.41) --
	(241.54,540.41) --
	(241.54,539.65) --
	(254.72,539.65) --
	(254.72,538.88) --
	(267.89,538.88) --
	(267.89,538.12) --
	(281.07,538.12) --
	(281.07,537.37) --
	(294.25,537.37) --
	(294.25,536.59);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 31.37,463.90) rectangle (306.77,554.59);
\end{scope}
\begin{scope}
\path[clip] ( 31.37,367.70) rectangle (306.77,458.40);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 31.37,367.70) rectangle (306.77,458.40);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,387.00) --
	(306.77,387.00);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,413.91) --
	(306.77,413.91);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,440.82) --
	(306.77,440.82);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 63.65,367.70) --
	( 63.65,458.40);

\path[draw=drawColor,line width= 0.3pt,line join=round] (129.54,367.70) --
	(129.54,458.40);

\path[draw=drawColor,line width= 0.3pt,line join=round] (195.42,367.70) --
	(195.42,458.40);

\path[draw=drawColor,line width= 0.3pt,line join=round] (261.31,367.70) --
	(261.31,458.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,373.54) --
	(306.77,373.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,400.45) --
	(306.77,400.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,427.36) --
	(306.77,427.36);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,454.28) --
	(306.77,454.28);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.59,367.70) --
	( 96.59,458.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.48,367.70) --
	(162.48,458.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.36,367.70) --
	(228.36,458.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (294.25,367.70) --
	(294.25,458.40);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,454.28) --
	( 57.06,454.28) --
	( 57.06,454.28) --
	( 70.24,454.28) --
	( 70.24,454.28) --
	( 83.42,454.28) --
	( 83.42,452.60) --
	( 96.59,452.60) --
	( 96.59,450.43) --
	(109.77,450.43) --
	(109.77,448.06) --
	(122.95,448.06) --
	(122.95,446.01) --
	(136.12,446.01) --
	(136.12,443.61) --
	(149.30,443.61) --
	(149.30,441.41) --
	(162.48,441.41) --
	(162.48,439.32) --
	(175.66,439.32) --
	(175.66,437.19) --
	(188.83,437.19) --
	(188.83,435.05) --
	(202.01,435.05) --
	(202.01,432.88) --
	(215.19,432.88) --
	(215.19,431.00) --
	(228.36,431.00) --
	(228.36,429.13) --
	(241.54,429.13) --
	(241.54,427.20) --
	(254.72,427.20) --
	(254.72,425.17) --
	(267.89,425.17) --
	(267.89,423.32) --
	(281.07,423.32) --
	(281.07,421.41) --
	(294.25,421.41) --
	(294.25,414.38);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,454.28) --
	( 57.06,454.28) --
	( 57.06,454.28) --
	( 70.24,454.28) --
	( 70.24,454.28) --
	( 83.42,454.28) --
	( 83.42,453.04) --
	( 96.59,453.04) --
	( 96.59,451.72) --
	(109.77,451.72) --
	(109.77,450.26) --
	(122.95,450.26) --
	(122.95,448.67) --
	(136.12,448.67) --
	(136.12,447.00) --
	(149.30,447.00) --
	(149.30,445.22) --
	(162.48,445.22) --
	(162.48,443.53) --
	(175.66,443.53) --
	(175.66,441.81) --
	(188.83,441.81) --
	(188.83,440.18) --
	(202.01,440.18) --
	(202.01,438.43) --
	(215.19,438.43) --
	(215.19,436.93) --
	(228.36,436.93) --
	(228.36,435.30) --
	(241.54,435.30) --
	(241.54,433.70) --
	(254.72,433.70) --
	(254.72,432.03) --
	(267.89,432.03) --
	(267.89,430.48) --
	(281.07,430.48) --
	(281.07,428.93) --
	(294.25,428.93) --
	(294.25,423.11);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,454.28) --
	( 57.06,454.28) --
	( 57.06,454.19) --
	( 70.24,454.19) --
	( 70.24,454.04) --
	( 83.42,454.04) --
	( 83.42,453.83) --
	( 96.59,453.83) --
	( 96.59,453.55) --
	(109.77,453.55) --
	(109.77,453.23) --
	(122.95,453.23) --
	(122.95,452.86) --
	(136.12,452.86) --
	(136.12,452.42) --
	(149.30,452.42) --
	(149.30,451.93) --
	(162.48,451.93) --
	(162.48,451.37) --
	(175.66,451.37) --
	(175.66,450.75) --
	(188.83,450.75) --
	(188.83,450.11) --
	(202.01,450.11) --
	(202.01,449.41) --
	(215.19,449.41) --
	(215.19,448.68) --
	(228.36,448.68) --
	(228.36,447.85) --
	(241.54,447.85) --
	(241.54,446.97) --
	(254.72,446.97) --
	(254.72,446.05) --
	(267.89,446.05) --
	(267.89,445.11) --
	(281.07,445.11) --
	(281.07,444.11) --
	(294.25,444.11) --
	(294.25,443.13);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,454.28) --
	( 57.06,454.28) --
	( 57.06,454.20) --
	( 70.24,454.20) --
	( 70.24,454.09) --
	( 83.42,454.09) --
	( 83.42,453.92) --
	( 96.59,453.92) --
	( 96.59,453.71) --
	(109.77,453.71) --
	(109.77,453.45) --
	(122.95,453.45) --
	(122.95,453.14) --
	(136.12,453.14) --
	(136.12,452.78) --
	(149.30,452.78) --
	(149.30,452.39) --
	(162.48,452.39) --
	(162.48,451.94) --
	(175.66,451.94) --
	(175.66,451.45) --
	(188.83,451.45) --
	(188.83,450.91) --
	(202.01,450.91) --
	(202.01,450.34) --
	(215.19,450.34) --
	(215.19,449.73) --
	(228.36,449.73) --
	(228.36,449.08) --
	(241.54,449.08) --
	(241.54,448.39) --
	(254.72,448.39) --
	(254.72,447.66) --
	(267.89,447.66) --
	(267.89,446.90) --
	(281.07,446.90) --
	(281.07,446.10) --
	(294.25,446.10) --
	(294.25,445.28);
\definecolor{drawColor}{RGB}{248,118,109}
